
---
title: "Wastewater Analysis"
author: "Eseza Kironde and Zoli Smith"
output:
  html_document
---

```{r set chunk options, echo = FALSE}
library(knitr)
opts_chunk$set(echo = FALSE,
               warning = FALSE,
               message = FALSE
)

```

# Introduction

Wastewater surveillance has emerged as a critical epidemiological tool for tracking infectious disease spread, particularly during the SARS-CoV-2 pandemic. This analysis of the National Wastewater Surveillance System (NWSS) dataset provides a comprehensive examination of COVID-19 viral concentrations across different geographic regions. By analyzing SARS-CoV-2 RNA levels in wastewater, we offer an innovative approach to monitoring community viral prevalence that complements traditional clinical testing methods.

# Data
Our research utilizes the Centers for Disease Control and Prevention (CDC) wastewater surveillance dataset, capturing a comprehensive time history of SARS-CoV-2 concentrations as of March 7, 2025. The dataset provides a unique perspective on viral transmission by analyzing genetic material found in wastewater treatment plants and upstream collection sites.

## Descriptive Analysis

```{r, summary-stats}
#read in the object we outputted
table_one <- readRDS(
  file = here::here("output/table_one.rds")
)

#print object
table_one
```




## Time series plot

```{r, time-series}

```









